---
title: "GBP_Corona_analysis"
author: "Minal Singhania"
date: "19/11/2023"
output: pdf_document
---

source required libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(survey)
library(dplyr)
library(tidyr)
library(stringr)
library(tableone)
library(ggplot2)
library(stats)
library(srvyr)
library(MatchIt)
library(lmtest)
library(sandwich)
library(Rcpp)
library(tidyverse)
library(survey)
```

Documentation on variables used.
ccgic1 - legal form of the company    
ccgic2 - annual revenue in previous calendar year
ccgic3 - category for revenue
ccgic6 - no of employees
industry_WZ08 - industry classification

corona relief measures

cgm1 Corona emergency relief
cgm2 interim aid
cgm3 short-time work/ allowance
cgm7 KfW special program
cgm9 others
cgm10 no measures requested/received
cgm11 refund tax prepayment for 2020
cgm12 immediate loss carryback
cgm13 deferral tax payments
cgm401 new start assistance

variables to capture dates when the funds have been requested
cgm1_H_1_2020, cgm1_H_2_2020, cgm1_H_1_2021, cgm1_H_2_2021 


Key KPI used to which are the dependent variables
ccd1 - Expected change in revenue in %
ccd2 _ Expected change in profit in % 
ccd9 - Expected change in investment in %
ccd6 - Expected change in employee count 

Information if received funds are sufficient to survive. 
cgm27 - Funds were sufficient,
cgm28 & cgm29 - Funds not sufficient,
cgm30 - No information

Select required variables and filter on wave 4
For cgm1 to cgm13( Aid provided to the company) there are 5 variables depicting time period when the Aid was given, select the date corresponding when Aid was provided.

perform data cleanup by replacing 9998, 9996 etc to NA

```{r Data Prepration}
#data <- read.csv("~/Documents/Project_Consulting/gbp_data.csv")

data <- read.csv("C:/Users/Minal/gbp_data.csv")

data_sel <- data %>% filter(wave==4)%>% select(gbpid, StartDate, EndDate, AGS, PLZ, weight, ccgic3, ccgic6, industry_WZ08,
                                               cgm1, cgm2, cgm3, cgm7, cgm9, cgm10, cgm11, cgm12, cgm13, 
                                               cos30,	cos31,	cos32,	cos33,	cos34,	cos35,	cos36,	cos37,	cos38,	cos39,
                                               ccd0, ccd1, ccd2, ccd9, ccd6,
                                               cgm401, cgm1_H_1_2020, cgm1_H_2_2020, cgm1_H_1_2021, cgm1_H_2_2021, cgm1_H_1_2022,
                                               cgm2_H_1_2020, cgm2_H_2_2020, cgm2_H_1_2021, cgm2_H_2_2021, cgm2_H_1_2022,
                                               cgm3_H_1_2020, cgm3_H_2_2020, cgm3_H_1_2021, cgm3_H_2_2021, cgm3_H_1_2022,
                                               cgm7_H_1_2020, cgm7_H_2_2020, cgm7_H_1_2021, cgm7_H_2_2021, cgm7_H_1_2022,
                                               cgm9_H_1_2020, cgm9_H_2_2020, cgm9_H_1_2021, cgm9_H_2_2021, cgm9_H_1_2022,
                                               cgm11_H_1_2020, cgm11_H_2_2020, cgm11_H_1_2021, cgm11_H_2_2021, cgm11_H_1_2022,
                                               cgm12_H_1_2020, cgm12_H_2_2020, cgm12_H_1_2021, cgm12_H_2_2021, cgm12_H_1_2022,
                                               cgm13_H_1_2020, cgm13_H_2_2020, cgm13_H_1_2021, cgm13_H_2_2021, cgm13_H_1_2022,
                                               cgm401_H_1_2020, cgm401_H_2_2020, cgm401_H_1_2021, cgm401_H_2_2021, cgm401_H_1_2022, cgm27, cgm28, cgm29, cgm30)%>%
  mutate(ccgic3 = gsub("Dropout",0,gsub("Refusal", 0, gsub("Does not apply", 0, gsub("I dont know", 0, ccgic3)))),
         ccd1 = gsub("Dropout",NA,gsub("Refusal", NA, gsub("Does not apply", NA, gsub("I dont know", NA, ccd1)))),
         ccd2 = gsub("Dropout",NA,gsub("Refusal", NA, gsub("Does not apply", NA, gsub("I dont know", NA, ccd2)))),
         ccd6 = gsub("Dropout",NA,gsub("Refusal", NA, gsub("Does not apply", NA, gsub("I dont know", NA, ccd6)))),
         ccd9 = gsub("Dropout",NA,gsub("Refusal", NA, gsub("Does not apply", NA, gsub("I dont know", NA, ccd9)))),
         AGS = as.character(AGS),
         across(c(cgm1_H_1_2020, cgm1_H_2_2020, cgm1_H_1_2021, cgm1_H_2_2021, cgm1_H_1_2022,
                  cgm2_H_1_2020, cgm2_H_2_2020, cgm2_H_1_2021, cgm2_H_2_2021, cgm2_H_1_2022,
                  cgm3_H_1_2020, cgm3_H_2_2020, cgm3_H_1_2021, cgm3_H_2_2021, cgm3_H_1_2022,
                  cgm7_H_1_2020, cgm7_H_2_2020, cgm7_H_1_2021, cgm7_H_2_2021, cgm7_H_1_2022,
                  cgm9_H_1_2020, cgm9_H_2_2020, cgm9_H_1_2021, cgm9_H_2_2021, cgm9_H_1_2022,
                  cgm11_H_1_2020, cgm11_H_2_2020, cgm11_H_1_2021, cgm11_H_2_2021, cgm11_H_1_2022,
                  cgm12_H_1_2020, cgm12_H_2_2020, cgm12_H_1_2021, cgm12_H_2_2021, cgm12_H_1_2022,
                  cgm13_H_1_2020, cgm13_H_2_2020, cgm13_H_1_2021, cgm13_H_2_2021, cgm13_H_1_2022,
                  cgm401_H_1_2020, cgm401_H_2_2020, cgm401_H_1_2021, cgm401_H_2_2021, cgm401_H_1_2022, ccd9, ccd6, industry_WZ08, AGS, cgm27, cgm28, cgm29, cgm30), function(x) ifelse((x=="-9996" |x=="-9997" |x=="-9998" | x=="-9999" |is.na(x) | x==""), NA, x))
        )
      
      drop_col <- colnames(data_sel[10:83]) # Create a list of columns which are not needed in the final dataset and already converted to categorical variables
      
      
      
       data_cat<- data_sel%>% mutate(Revenue_prevYr = case_when(ccgic3 %in% c(1,2,3,4,5,6,7,8,9,10,11,12,13,14) ~ ccgic3,
                                                                 TRUE  ~ NA), 
                                    
                                    EmployeeCNT_cat = case_when(ccgic6 <= 5 ~ "Small",
                                                                ccgic6 == 6 ~"Medium",
                                                                ccgic6 > 6 ~ "Large")%>% as.factor(),
                                    
                                    company_size = case_when((ccgic3 <= 5 & ccgic6 <= 3) ~ "Micro",
                                                              (ccgic3 <= 8 & ccgic6 <= 5) ~ "Small",
                                                              (ccgic3 <= 12 & ccgic6 <= 6) ~ "Medium",
                                                              (ccgic3 > 12 | ccgic6 > 6) ~ "Large",
                                                              TRUE  ~ "Others")%>% as.factor(), #define company size using European community 2003 guidelines
                                    
                                    industry_WZ08_cat = ifelse(!is.na(industry_WZ08) ,substr(industry_WZ08,1,1), NA )%>% as.factor(),
                                    fed_state = ifelse(!is.na(AGS), substr(str_pad(AGS,8, "left", '0'), 1,2), NA),
                                    # LL: I changed it the below variables to numeric, which is prepared for plot creating
                                    Change_Revenue = ccd1%>% as.numeric(),
                                    Change_Employee_CNT =ccd2%>% as.numeric(),
                                    Change_Investment =ccd9%>% as.numeric(),
                                   
                                    Change_profit = ccd6%>% as.numeric(),
                                    
                                   
                                    
                                    Aid_EmergencyRf = ifelse(cgm1 %in% c('1', '0'), cgm1, 0 ),
                                    Aid_Interim = ifelse(cgm2 %in% c('1', '0'), cgm2, 0 ),
                                    Aid_Allowance = ifelse(cgm3 %in% c('1', '0'), cgm3, 0 ),
                                    Aid_KfW = ifelse(cgm7 %in% c('1', '0'), cgm7, 0 ),
                                    Aid_Others = ifelse(cgm9 %in% c('1', '0'), cgm9, 0 ),
                                    Aid_TaxRefund = ifelse(cgm11 %in% c('1', '0'), cgm11, 0 ),
                                    Aid_LossCarry = ifelse(cgm12 %in% c('1', '0'), cgm12, 0 ),
                                    Aid_Deferral = ifelse(cgm13 %in% c('1', '0'), cgm13, 0 ),
                                    Aid_NewAssistance = ifelse(cgm401 %in% c('1', '0'), cgm401, 0 ),
                                    
                                                                  
                                    #Capture if the received Aid was sufficient to overcome the crisis
                                    Survival = case_when(cgm27 == 1 ~ 'Sufficient',
                                                         (cgm28 == 1 | cgm29 == 1) ~ 'Not Sufficient',
                                                         TRUE ~ 'No info')
                                    
      )%>%select(-drop_col)
      
      
      
      # Add information on Industry classification
      
      Industry <- data.frame(IndustryDef = c('Agriculture, forestry, and fishing',
                                             'Mining and quarrying',
                                             'Manufacturing',
                                             'Electricity, gas, steam, and air-conditioning supply',
                                             'Water supply, sewerage, waste management, and remediation',
                                       'Construction',
                                       'Wholesale and retail trade, repair of motor vehicles and motorcycles',
                                       'Transportation and storage',
                                       'Accommodation and food service',
                                       'Information and communication',
                                       'Financial and insurance',
                                       'Real estate',
                                       'Professional, scientific, and technical',
                                       'Administrative and support service',
                                       'Public administration and defence, social security',
                                       'Education',
                                       'Human health and social work',
                                       'Arts, entertainment, recreation',
                                       'Other services',
                                       'Households as employers',
                                       'Extra-territorial organisations and bodies'),
                       Industry_cat = c('A','B', 'C', 'D', 'E', 'F', 'G', 'H', 'I', 'J', 'K', 'L','M', 'N', 'O', 'P', 'Q', 'R', 'S', 'T', 'U'))
data_cat1 <- data_cat %>% left_join(Industry, by = c("industry_WZ08_cat" ="Industry_cat")) %>% select(-c( ccgic3, ccgic6)) %>%
  
# define variable funding when one of the 3 interested funds were opted by the companies 
  
           mutate(Funding = case_when(((Aid_EmergencyRf =='1' & !is.na(Aid_EmergencyRf))| (Aid_Allowance=='1' & !is.na(Aid_Allowance)) |(Aid_KfW =='1' & !is.na(Aid_KfW)))  ~ 1,
                                    ((Aid_Others =='1' & !is.na(Aid_Others)) | (Aid_TaxRefund =='1' & !is.na(Aid_TaxRefund)) | (Aid_LossCarry =='1' & !is.na(Aid_LossCarry)) |  (Aid_Interim =='1' & !is.na(Aid_Interim)) | (Aid_Deferral =='1' & !is.na(Aid_Deferral)) | (Aid_NewAssistance =='1' & !is.na(Aid_NewAssistance)))  ~ 2, 
                                    TRUE ~ 0)%>% as.factor(),
                  
  
               
         Funding_bin = paste0(Aid_KfW ,Aid_EmergencyRf, Aid_Allowance),
         fed_state = case_when(fed_state == "01" ~ "Schleswig-Holstein",
                               fed_state == "02" ~ "Hamburg",
                               fed_state == "03" ~ "Niedersachsen",
                               fed_state == "04" ~ "Bremen",
                               fed_state == "05" ~ "Nordrhein-Westfalen",
                               fed_state == "06" ~ "Hessen",
                               fed_state == "07" ~ "Rheinland-Pfalz",
                               fed_state == "08" ~ "Baden-Wuerttemberg",
                               fed_state == "09" ~ "Bayern",
                               fed_state == "10" ~ "Saarland",
                               fed_state == "11" ~ "Berlin",
                               fed_state == "12" ~ "Brandenburg",
                               fed_state == "13" ~ "Mecklenburg",
                               fed_state == "14" ~ "Sachsen",
                               fed_state == "15" ~ "Sachsen-Anhalt",
                               fed_state == "16" ~ "Thuringen",
                               TRUE ~ "Not Specified"),
         
  #Collape industrial sectors into broader areas       
         industry_sec = case_when(
                            (industry_WZ08_cat == 'A') ~ 'Agriculture',
                            (industry_WZ08_cat == 'C') ~ 'Manufacturing',
                            (industry_WZ08_cat == 'F') ~ 'Construction',
                            (industry_WZ08_cat %in% c('B','D', 'E')) ~ 'Mining, Elec, Water',
                            (industry_WZ08_cat %in% c('G', 'H', 'I', 'J', 'K', 'L', 'M', 'N')) ~ 'Market Services',
                            (industry_WZ08_cat %in% c('O', 'P', 'Q', 'R', 'S', 'T', 'U', 'V')) ~ 'Non Market Services',
                            TRUE ~ 'Others')
         
                            
        
                                  ) %>% select (-c( industry_WZ08_cat, industry_WZ08)) 



#data_cat1$Funding <- factor(data_cat1$Funding, levels = c(0,1), labels = c("No", "Yes"))

```



## Create Data descriptives

```{r Count Check}

data %>% filter(wave==4) %>% count()

data_cat1 %>% count()

```



```{r Data filteration}
#Filter for missing or incomplete data and funding types which we are not interested 
data_cat1 <- data_cat1 %>% filter(Funding != 2) %>% filter(industry_sec != "Mining, Elec, Water", company_size != "Others", fed_state != 'Not Specified') 


data_cat1 %>% count()


```

Create Survey design using weight
```{r create survey design using weights}

#Create dataframe using survey design
data_kpi <-data_cat1[!is.na(data_cat1$weight),]
#data_survey <- data_kpi %>% as_survey(weights = c(weight)) %>% as.data.frame()
data_survey <- data_kpi %>% as_survey(weights = c(weight))

# count of records after applying weights
data_kpi %>% count()

```

## Perform Exploratory data analysis
```{r Descriptives for different Fundings with weight"}

cols = c("Funding_bin" , "Funding", "Survival", "industry_sec" , "company_size", "Aid_EmergencyRf", "Aid_Interim", "Aid_Allowance",
                                    "Aid_KfW" ,
                                    "Aid_Others" ,
                                    "Aid_TaxRefund" ,
                                    "Aid_LossCarry" ,
                                    "Aid_Deferral",
                                    "Aid_NewAssistance", "fed_state")
for(i in seq_along(cols)){
FORMULA= as.formula(paste("~",cols[i]))
print(svytable(FORMULA, design= data_survey)) }
print(prop.table(svytable(FORMULA, design= data_survey)))


```



```{r Create Data descriptives using weights}



table1 <- data_kpi %>%
  as_survey(weights = c(weight)) %>%
  group_by(Funding ) %>%
  summarise_at(vars(Change_Revenue, Change_profit), list(name = survey_mean), na.rm=TRUE)

table1



```




```{r revenue distribution with and without funding weights}

med_chg_revenue <- data_survey[, c("Funding", "Change_Revenue")] %>% 
  group_by(Funding) %>%
  summarize(median=survey_mean(Change_Revenue, na.rm = T))


data_cat1 %>% filter(!is.na(Change_Revenue), !is.na(weight) ) %>% group_by(Funding) %>% 
ggplot( mapping =aes(x = Change_Revenue, weight = weight, color = Funding))+  geom_density() + 
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected Revenue Change",
       subtitle="Expected Revenue Change with and without Funding")+
  theme(legend.position="bottom")+
  geom_vline(data=med_chg_revenue, aes(xintercept=median, color=Funding),
             linetype="dashed")




```



```{r histogram change profit}
svyhist(~Change_Revenue,design = data_survey,
breaks = c(-100,-50,  -20, -10, 0,10, 20, 50,100),
main="Distribution of Change in Revenue",
xlab="Change in Revenue"
)

svyhist(~Change_profit,design = data_survey,
breaks = c(-100,-50, -20, -10, 0,10, 20, 50,100),
main="Distribution of Change in Profit",
xlab="Change in Profit"
)
```



```{r Weighted profit distribution with and without funding }

med_chg_profit <- data_survey[, c("Funding", "Change_profit")] %>% 
  group_by(Funding) %>%
  summarize(median=survey_mean(Change_profit, na.rm = T))



data_cat1 %>% filter(!is.na(Change_profit), !is.na(weight) ) %>% group_by(Funding) %>% 
ggplot( mapping =aes(x = Change_profit, weight = weight, color = Funding))+  geom_density() + 
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected Profit Change",
       subtitle="Expected Profit Change with and without Funding")+
  theme(legend.position="bottom")+
  geom_vline(data=med_chg_profit, aes(xintercept=median, color=Funding),
             linetype="dashed")


```



```{r Weighted Aid vs Industry sector}

out_indstry <- data_survey[, c("industry_sec", "Funding")] %>% 
group_by(col1 = factor(industry_sec), Funding) %>%  
  summarize(n = survey_total(na.rm = T)) %>% as.data.frame()

out_indstry %>% mutate(col4 = prop.table(n)) %>%  
  ggplot(aes(x = col1, y = col4, fill = Funding, label = scales::percent(col4))) +  
  geom_col(position = 'dodge') +  
  geom_text(aes(x = col1, y = col4, fill = Funding, label = scales::percent(col4)), vjust= 0.5,hjust= 0, size = 3, position = position_dodge(width = 1) ) +  
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(y="Percentage", x="Industrial Sector", title="Allocation of Funding across different Industries")+ theme_minimal()+
theme(plot.title = element_text(hjust = 1.0))

```




```{r weighted Aid vs Company size}

out_company <- data_survey[, c("company_size", "Funding")] %>% 
group_by(col1 = factor(company_size), Funding) %>%  
  summarize(n = survey_total(na.rm = T)) %>% as.data.frame()

  out_company %>% mutate(col4 = prop.table(n)) %>%  
  ggplot(aes(x = col1, y = col4, fill = Funding, label = scales::percent(col4))) +  
  geom_col(position = 'dodge') +  
  geom_text(aes(x = col1, y = col4, fill = Funding, label = scales::percent(col4)), vjust= 0.5,hjust= 0, size = 3, position = position_dodge(width = 1) ) +  
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(y="Percentage", x="Company Size", title="Allocation of Funding based on Company Size")+ theme_minimal()+
theme(plot.title = element_text(hjust = 1.0))

```



```{r Aid vs Federal state}


data_survey[, c("fed_state", "Funding")] %>% 
group_by(col1 = factor(fed_state), Funding) %>%  
  summarize(n = survey_total(na.rm = T)) %>%
  mutate(col4 = prop.table(n)) %>%  
  ggplot(aes(x = col1, y = col4, fill = Funding, label = scales::percent(col4))) +  
  geom_col(position = 'dodge') +  
  geom_text(aes(x = col1, y = col4, fill = Funding, label = scales::percent(col4)), vjust= 0.5,hjust= 0, size = 3, position = position_dodge(width = 1) ) +  
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(y="Percentage", x="Federal State", title="Allocation of Funding across federal states of Germany")+ theme_minimal()+
theme(plot.title = element_text(hjust = 1.0))



```





```{r proportion table between Industry and company size}


table_ind_xtabs <- svytable(~industry_sec +company_size, data_survey)
round(prop.table(table_ind_xtabs,),2)


```

```{r box plot revenue distribution across company size using weights}

ggplot(data_cat1[data_cat1$Funding ==c(0,1), ], aes(x = factor(Funding), y = Change_Revenue, weight = weight ))+  geom_boxplot() + 
  facet_grid(~company_size)
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected Revenue Change",
       subtitle="Expected Revenue Change with and without Funding")+
  theme(legend.position="bottom")
  
```

```{r box plot profit distribution across company size using weights}

ggplot(data_cat1[data_cat1$Funding ==c(0,1), ], aes(x = factor(Funding), y = Change_profit, weight = weight ))+  geom_boxplot() + 
  facet_grid(~company_size)
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected Profit Change",
       subtitle="Expected Profit Change with and without Funding")+
  theme(legend.position="bottom")
  
```

```{r box plot profit distribution across industries using weights 1}
ggplot(data_cat1[data_cat1$Funding ==c(0,1), ], aes(x = factor(Funding), y = Change_profit, weight = weight))+  geom_boxplot() + 
  facet_grid(~industry_sec)
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected profit Change",
       subtitle="Expected profit Change with and without Funding")+
  theme(legend.position="bottom")
```  


```{r box plot revenue distribution across industries using weights 1}
ggplot(data_cat1[data_cat1$Funding ==c(0,1), ], aes(x = factor(Funding), y = Change_Revenue, weight = weight))+  geom_boxplot() + 
  facet_grid(~industry_sec)
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected profit Change",
       subtitle="Expected revenue Change with and without Funding")+
  theme(legend.position="bottom")
```  
  
```{r Revenue Change with fundings vs without fundings in different Industries}

table1 <- data_kpi %>%
  as_survey(weights = c(weight)) %>%
  group_by(Funding,industry_sec ) %>%
  summarise_at(vars(Change_Revenue), list(name = survey_mean), na.rm=TRUE)


table1$Funding<-factor(table1$Funding,levels = c("0","1"),labels = c("No","Yes"))


ggplot(data=table1, aes(x=name_se, y=industry_sec)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(x = name_se, y = industry_sec,  label = round(name_se,2)), vjust= 0,hjust= 0, size = 3, position = position_dodge(width = 0.5) ) +  
  scale_fill_brewer(palette="Paired")+
  facet_grid(~Funding) +
  labs(x="Revenue Change in %", y="Industry", title="Industry Revenue Change: Aid vs.No Aid Distribution") +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 1))

```

```{r Profit Change with fundings vs without fundings in different Industries}

table4 <- data_kpi %>%
  as_survey(weights = c(weight)) %>%
  group_by(Funding,industry_sec ) %>%
  summarise_at(vars(Change_profit), list(name = survey_mean), na.rm=TRUE)


table4$Funding<-factor(table4$Funding,levels = c("0","1"),labels = c("No","Yes"))

ggplot(data=table4, aes(x=name_se, y=industry_sec)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(x = name_se, y = industry_sec,  label = round(name_se,2)), vjust= 0,hjust= 0, size = 3, position = position_dodge(width = 0.5) ) +  
  scale_fill_brewer(palette="Paired")+
  facet_grid(~Funding) +
  labs(x="Profit Change in %", y="Industry", title="Industry Profit Change: Aid vs.No Aid Distribution") +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 1))
```

```{r Revenue Change with fundings vs without fundings in across Company sizes}

table2 <- data_kpi %>%
  as_survey(weights = c(weight)) %>%
  group_by(Funding,company_size ) %>%
  summarise_at(vars(Change_Revenue), list(name = survey_mean), na.rm=TRUE)


table2$Funding<-factor(table2$Funding,levels = c("0","1"),labels = c("No","Yes"))

# Revenue Change: with fundings vs without fundings in different Industries

ggplot(data=table2, aes(x=name_se, y=company_size)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(x = name_se, y = company_size,  label = round(name_se,2)), vjust= 0,hjust= 0, size = 3, position = position_dodge(width = 0.5) ) +  
  scale_fill_brewer(palette="Paired")+
  facet_grid(~Funding) +
  labs(x="Revenue Change in %", y="Company Size ", title="Industry Revenue Change with size:Aid vs.No Aid Distribution") +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 1))
```

```{r Profit Change with fundings vs without fundings in across Company sizes}
table3 <- data_kpi %>%
  as_survey(weights = c(weight)) %>%
  group_by(Funding,company_size ) %>%
  summarise_at(vars(Change_profit), list(name = survey_mean), na.rm=TRUE)


table3$Funding<-factor(table3$Funding,levels = c("0","1"),labels = c("No","Yes"))

ggplot(data=table3, aes(x=name_se, y=company_size)) +
  geom_bar(stat="identity", position=position_dodge())+
  geom_text(aes(x = name_se, y = company_size,  label = round(name_se,2)), vjust= 0,hjust= 0, size = 3, position = position_dodge(width = 0.5) ) +  
  scale_fill_brewer(palette="Paired")+
  facet_grid(~Funding) +
  labs(x="Profit Change in %", y="Company Size", title="Industry Profit Change with size: Aid vs.No Aid Distribution") +
  theme_minimal()+
  theme(plot.title = element_text(hjust = 1))
```


## LOGIT Model
Perform logistic regression to see if company size and industry type have any corelation to who receives the funding.

```{r  logit model}

fundlogit <- svyglm( Funding ~ industry_sec + company_size, design =data_survey, family = "binomial")
summary(fundlogit)
confint(fundlogit)
#wald.test(b= coef(fundlogit), Sigma = vcov(fundlogit), Terms = 2:5)
```

## Regression Analysis

Perform regression analysis to see how revenue and profit changes due to Aids provided, Industry type, Company size

```{r  regression analysis }

reg_revenue_wt <- svyglm( Change_Revenue ~Funding *( industry_sec + company_size), design =data_survey)
summary(reg_revenue_wt)

reg_profit_wt <- svyglm( Change_profit ~Funding * ( industry_sec + company_size), design =data_survey)
summary(reg_profit_wt)



```


## Propensity Score matching

```{r create PSM groups}

data_psm <- data_cat1 %>% select(Funding  ,industry_sec, company_size , Change_Revenue, weight) %>% drop_na()

match_obj <- matchit(Funding ~  industry_sec + company_size  ,
                     data = data_psm, method = "nearest", distance ="glm",
                     
                     replace = FALSE
                     )
summary(match_obj)
#plotting the balance between those given funding and others which didn't get

plot(match_obj, type = "hist", interactive = FALSE)
plot(summary(match_obj), abs = FALSE)



matched_data <- match.data(match_obj)

res <- lm(Change_Revenue ~  Funding *( industry_sec + company_size) , data= matched_data, weights = weight )
summary(res)

#profit

data_psm_prof <- data_cat1 %>% select(Funding ,industry_sec, company_size , Change_profit, weight) %>% drop_na()

match_obj1 <- matchit(Funding ~  industry_sec + company_size  ,
                     data = data_psm_prof, method = "nearest", distance ="glm",
                     
                     replace = FALSE
                     )
summary(match_obj1)
#plotting the balance between those given funding and others which didn't get

plot(match_obj1, type = "hist", interactive = FALSE)
plot(summary(match_obj1), abs = FALSE)



matched_data1 <- match.data(match_obj1)
res_profit <- lm(Change_profit ~  Funding *( industry_sec + company_size) , data= matched_data1, weights = weight )
summary(res_profit)


```




```{r revenue distribution with and without funding weights on matched data}


matched_data  %>% 
ggplot( mapping =aes(x = Change_Revenue, weight = weight, color = Funding))+  geom_density() + 
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected Revenue Change",
       subtitle="Expected Revenue Change with and without Funding")+
  theme(legend.position="bottom")


matched_data1  %>% 
ggplot( mapping =aes(x = Change_profit, weight = weight, color = Funding))+  geom_density() + 
  #scale_color_manual(values = c("#868686FF", "#EFC000FF"))+
  labs(x= "Expected Profit Change",
       subtitle="Expected Profit Change with and without Funding")+
  theme(legend.position="bottom")



```






